Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-21 manuscript/draft_rsfmri.Rmd
clean up: figures + tables are created in other scripts

```{r tableSample, echo=FALSE}
tab_sample <-
  knitr::kable(
    tab_sample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Distribution of data points at months after intervention")
tab_sample
```

@@

# table for descriptive statistics
descr <- psych::describeBy(dfw[,5:ncol(dfw)], group=dfw$condition,mat=T)
descr$predictor <- c(rep("BMI",6),rep("meanFD",6))
descr$tp <- car::recode(descr$vars, "c(1,4)='fu2';c(2,5)='fu';c(3,6)='bl'")
descr$group <- descr$group1
descr <- descr[,c("predictor","tp","group","n","mean","sd")]
descr <- descr[with(descr, order(predictor, tp)),]
descr[,c("mean","sd")] <- round(descr[,c("mean","sd")],2)
descr[c(2:6,8:12),"predictor"] <- ""
descr[c(2,4,6,8,10,12),"tp"] <- ""
rownames(descr) <- NULL

@@

```
<!-- STUDY PROCEDURE --> Subjects arrived in the morning (between 07:00 and 12:00) after an overnight fast. They underwent medical assessments including an interview, blood draw and anthropometric measurements before having a one our break for <!-- standadized??  -->breakfast. MRI scanning was done after further psychological tests (for details see @Prehn_2020).
```{r figBMIdescr, fig.align='center', out.width="90%", fig.cap="BMI over time.", echo=FALSE}
# eval = TRUE, fig.asp = 0.7, fig.width = 6
condition.labs <- c("BARS","NBARS")
names(condition.labs) <- c("IG","KG")
# BMI over time each group
figBMIdescr <-
  ggplot(final, aes(
    x = tp,
    y = BMI,
    group = subj.ID,
    color = condition
  )) +
  geom_line() + geom_point() +
  stat_summary(
    aes(group = condition),
    fun = mean,
    geom  = "line",
    size = 2,
    color = c(rep("#00305E", 3), rep("#C00045", 3))
  ) +
  facet_grid(. ~ condition, labeller = labeller(condition=condition.labs)) + xlab("time points")
figBMIdescr +
  scale_x_discrete(labels = c("bl" = "0", "fu" = "6", "fu2" = "12")) +
  scale_color_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")
  ) +
  xlab("Time after intervention [months]") + ylab ("BMI [kg/m²]") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.position = "none"
  )
```

@@

<!-- DESIGN MATRIX, vielleicht beide auch als Abbildung kurz zeigen? --> For the first model, time was introduced as factor because we did not assume strict linearity for the increase in connectivity and therefore refrained from modeling time as continuous variable (see Figure \@ref(fig:figDesignmatrix)). The resulting factorial design <!-- check: flexible factorial? --> contained one regressor for each time point per group.
```{r figDesignmatrix, fig.align = 'center', fig.ncol = 2, out.width = "50%", fig.subcap=c('Design matrix with time as categorial factor.','Design matrix with time as continuous variable.'), fig.cap="Possible design matrices of time-by-group model.", echo=FALSE}
# fig.show="hold",  out.width="40%", fig.height = 8,

# design matrix time as factor
txt_path <- "/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /SwE_files/noExclFD/both/total/"

ID <- read.delim(paste0(txt_path,"subjID.txt"), head=FALSE)
condition <- read.delim(paste0(txt_path,"group.txt"), head=FALSE)
KG_bl <- read.delim(paste0(txt_path,"KG_bl.txt"), head=FALSE)
KG_fu <- read.delim(paste0(txt_path,"KG_fu.txt"), head=FALSE)
KG_fu2 <- read.delim(paste0(txt_path,"KG_fu2.txt"), head=FALSE)
IG_bl <- read.delim(paste0(txt_path,"IG_bl.txt"), head=FALSE)
IG_fu <- read.delim(paste0(txt_path,"IG_fu.txt"), head=FALSE)
IG_fu2 <- read.delim(paste0(txt_path,"IG_fu2.txt"), head=FALSE)
measurement <- c(1:nrow(ID))
dmf <- data.frame(measurement,ID,condition,KG_bl,KG_fu,KG_fu2,IG_bl,IG_fu,IG_fu2)
colnames(dmf) <- c("measurement","ID","condition","N0","N6","N12","B0","B6","B12")

# design matrix time as continuous variable
ID <- read.delim(paste0(txt_path,"subjID.txt"), head=FALSE)
condition <- read.delim(paste0(txt_path,"group.txt"), head=FALSE)
group_IG <- read.delim(paste0(txt_path,"group_IG.txt"), head=FALSE)
group_KG <- read.delim(paste0(txt_path,"group_KG.txt"), head=FALSE)
tp_IG <- read.delim(paste0(txt_path,"tp_IG.txt"), head=FALSE)
tp_KG <- read.delim(paste0(txt_path,"tp_KG.txt"), head=FALSE)
measurement <- c(1:nrow(ID))
dmc <- data.frame(measurement,ID,condition,group_IG,group_KG,tp_IG,tp_KG)
colnames(dmc) <- c("measurement","ID","condition","groupB", "groupN","timeB","timeN")

# plot dmf
input_dmf <- dmf %>%
  pivot_longer(
    cols= colnames(dmf[,c(4:ncol(dmf))]),
    names_to = "regressor")
input_dmc <- dmc %>%
  pivot_longer(
    cols= colnames(dmc[,c(4:ncol(dmc))]),
    names_to = "regressor")

plotA <- ggplot(input_dmf, aes(x = regressor, y = measurement, fill = value)) +
  geom_tile() +
  scale_fill_gradient(low="black", high="white") +
  labs(x="regressors", y="scans") +
  # design
  scale_x_discrete(expand = c(0,0),labels=colnames(dmf)[4:ncol(dmf)]) +
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() + theme(legend.position = "none",
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12))
# + theme(panel.grid = element_blank(),
#         panel.border = element_rect(colour = "black", size=1),
#    legend.text = element_text(size = 10)
#         plot.title=element_text(size=11))
plotB <- ggplot(input_dmc, aes(x = regressor, y = measurement, fill = value)) +
  geom_tile() +
  scale_fill_gradient(low="black", high="white") +
  labs(x="regressors", y="scans") +
  # design
  scale_x_discrete(expand = c(0,0),labels=colnames(dmc)[4:ncol(dmc)]) +
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() + theme(legend.position = "none",
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12))
# + theme(panel.grid = element_blank(),
#         panel.border = element_rect(colour = "black", size=1),
#    legend.text = element_text(size = 10)
#         plot.title=element_text(size=11))

plotA
plotB
#gridExtra::grid.arrange(plotA, plotB, nrow=1)
```
For the second and third model, we calculated the centered mean BMI and log mean FD per subject and the intra-subject-centered BMI as proposed by @Guillaume_2014. With a model containing average BMI and longitudinal change per subject, we investigated their differential effects on the complete sample and subsequently in a exploratory fashion for the intervention group only as the effect of longitudinal change in BMI was expected to be driven by this subsample.
<!-- NUISANCE COVARIATES --> Baseline age, sex, and log mean framewise displacement (FD) were entered into the first and second model as nuisance variables. Age and sex were between-subject covariates while FD is time-varying. Mean FD was log-transformed and age was demeaned by subtracting the overall mean across subjects and time points. 
As change in FD and change in BMI share common variance [@Beyer_2019], the inclusion of log mean FD may be disputed and done optionally. For that reason, we performed each analysis separately one with mean FD (three and without. Differences in results will be reported. We consider this sensitivity analysis theoretically more meaningful than the preregistered comparison with the nuisance covariate free model and a model with four nuisance covariates (including baseline BMI).<!-- Prereg: We will perform sensitivity analysis adjusting for baseline age, sex, average of mean FD of both time points and baseline BMI -->
<!-- POST HOC  --> For a better understanding of the unique contribution of average and longitudinal change FD measures, we separately employed a third post-hoc model to disentangle the effects: $FC = between-subject FD + within-subject FD$ with nuisance covariates age and sex. As these post-hoc analyses were not preregistered, they should be considered to be exploratory.

@@

for (i in 1:nrow(final)) {
  tmp = strsplit(toString(final[i, "scan_dir"]), '/')[[1]][8]
  conf = read.csv(
    paste0("/data/pt_02161/preprocessed/resting/detailedQA/metrics/",tmp,"/confounds.csv")
  )
  tmp = cor.test(conf$DVARS, conf$FD)
  final[i, "corr_DVARS_FD"] = tmp$estimate
  final[i, "mean_DVARS"] = mean(conf$DVARS, na.rm = TRUE)
  final[i, "max_DVARS"] = max(conf$DVARS, na.rm = TRUE)
  final[i, "mean_outliers"] = mean(conf$outliers, na.rm = TRUE)
}
```

```{r figDvarsmFD, fig.align = "center", out.width="100%", fig.cap='Summary of quality measures DVARS and mFD'}
# ,  fig.align='center', }
# eval = TRUE, fig.asp = 0.7, fig.width = 6
condition.labs <- c("BARS","NBARS")
names(condition.labs) <- c("IG","KG")

# DVARS over time each group
fig_DVARSdescr <-
  ggplot(final, aes(
    x = tp,
    y = mean_DVARS,
    group = subj.ID,
    color = condition
  )) +
  geom_line() + geom_point() +
  stat_summary(
    aes(group = condition),
    fun = mean,
    geom  = "line",
    size = 2,
    color = c(rep("#00305E", 3), rep("#C00045", 3))
  ) +
  facet_grid(. ~ condition, labeller = labeller(condition=condition.labs)) + xlab("time points")
fig1=fig_DVARSdescr +
  scale_x_discrete(labels = c("bl" = "0", "fu" = "6", "fu2" = "12")) +
  scale_color_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")
  ) +
  xlab("Time [months]") + ylab ("Mean DVARS") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.position = "none"
  )
# mFD over time each group
fig_mFDdescr <-
  ggplot(final, aes(
    x = tp,
    y = meanFD,
    group = subj.ID,
    color = condition
  )) +
  geom_line() + geom_point() +
  stat_summary(
    aes(group = condition),
    fun = mean,
    geom  = "line",
    size = 2,
    color = c(rep("#00305E", 3), rep("#C00045", 3))
  ) +
  facet_grid(. ~ condition, labeller = labeller(condition=condition.labs)) + xlab("time points")
fig2=fig_mFDdescr +
  scale_x_discrete(labels = c("bl" = "0", "fu" = "6", "fu2" = "12")) +
  scale_color_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")
  ) +
  xlab("Time [months]") + ylab ("mFD in mm") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.position = "none"
  )
# DVARS-FD over time each group
fig_mFDDVARSdescr <-
  ggplot(final, aes(
    x = tp,
    y = corr_DVARS_FD,
    group = subj.ID,
    color = condition
  )) +
  geom_line() + geom_point() +
  stat_summary(
    aes(group = condition),
    fun = mean,
    geom  = "line",
    size = 2,
    color = c(rep("#00305E", 3), rep("#C00045", 3))
  ) +
  facet_grid(. ~ condition, labeller = labeller(condition=condition.labs)) + xlab("time points")
fig3=fig_mFDDVARSdescr +
  scale_x_discrete(labels = c("bl" = "0", "fu" = "6", "fu2" = "12")) +
  scale_color_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")
  ) +
  xlab("Time [months]") + ylab ("DVARS-FD correlation") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.position = "none"
  )

(fig1 | fig2) / fig3

@@

tab_qc_fc <-
  knitr::kable(
    round(res,3),
    col.names = colnames(res),
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Summary of quality metrics for different denoising pipelines across conditions and time points") %>%
    column_spec(c(2:6), width = "1.8cm")

tab_qc_fc
```

@@

```{r tableBMImodel}
source("code/tables_FC.R")
TableList <- construct_FCtables()
tab_BMImodel <- TableList[[1]]
tab_BMImodel
```

@@

```{r Exploratory plots, eval=FALSE}
# BMI over time per group
tspag <-
  ggplot(final, aes(x = tp, y = BMI)) +
  stat_summary(
    aes(group = condition),
    fun = mean,
    geom  = "line",
    size = 2,
    color = c(rep("#00305E", 3), rep("#C00045", 3))
  ) +
  geom_line(aes(group = subj.ID, color = condition)) +
  geom_point(aes(color = condition))
tspag +
  scale_x_discrete(labels = c("bl" = "0", "fu" = "6", "fu2" = "12")) +
  scale_color_manual(
    values = c("#00305E77", "#C0004577"),
    labels = c("intervention", "control")
  ) +
  xlab("Time after intervention [months]") + ylab ("BMI [kg/m²]") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    legend.background = element_rect(colour = "grey")
  )

# BMI over time per subject
# group x time interaction for BMI
tspag <- ggplot(final, aes(
  x = tp,
  y = BMI,
  color = condition,
  group = condition
)) +
  geom_point() +

  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun = mean, geom = "line")
tspag  +
  scale_color_manual(values = c("#00305E", "#C00045")) +
  theme_bw() +
  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    legend.position = "top"
)
```

```{r expample plots, eval=FALSE}

df_wide <- tidyr::pivot_wider(
  data = final,
  id_cols = "subj.ID",
  names_from = "tp",
  values_from = c("tp", "BMI", "logmFD")
)

if (tp == "BLFU") {
  s = 2
} else {
  s = 1
}

BMI_vector <- c("BMI_fu2", "BMI_fu", "BMI_bl")
BMI_vector <- c("BMI_bl", "BMI_fu", "BMI_fu2")
FD_vector <- c("logmFD_fu2", "logmFD_fu", "logmFD_bl")
df_wide$avgBMI <- apply(df_wide[, BMI_vector[s:3]],
                        MARGIN = 1,
                        FUN = mean,
                        na.rm = TRUE)
df_wide$avgFD <- apply(df_wide[, FD_vector[s:3]],
                       MARGIN = 1,
                       FUN = mean,
                       na.rm = TRUE)
df_long <- tidyr::pivot_longer(
  data = df_wide,
  cols = all_of(order_vector),
  # bl, fu, fu2 (maintain original order)
  # CAREFUL: Order according to dataframe df
  names_to = "tp_tp",
  values_to = "tp",
  values_drop_na = TRUE
)
all(df_long$tp == final$tp) # check if order correct

head(final[, c("subj.ID", "tp")])
head(df_long[, c("subj.ID", "tp")])

df_long$cgnBMI <- final$BMI - df_long$avgBMI
df_long$avgBMIc <-
  df_long$avgBMI - mean(df_long$avgBMI, na.rm = TRUE)
df$avgBMIc <- df_long$avgBMIc
df$cgnBMI <- df_long$cgnBMI

df_long$cgnFD <- final$logmFD - df_long$avgFD
df_long$avgFDc <-
  df_long$avgFD - mean(df_long$avgFD, na.rm = TRUE)
final$avgFDc <- df_long$avgFDc
final$cgnFD <- df_long$cgnFD

# example plots for interaction effect (arbitrary variables for illustration purposes)
ggplot(final, aes(x=tp, y=BMI, group=condition, color=condition)) +
  #geom_smooth(aes(group=condition)) +
  stat_summary(fun = mean, geom = "point", size=3, shape=15) +
  stat_summary(fun = mean, geom = "line", size=1) +
  #scale_color_brewer(values = "Set1") +
  scale_x_discrete(labels=c("bl"= "0", "fu"= "6", "fu2" = "12")) +
  scale_color_manual(values=c("#00305E","#C00045"),labels = c("intervention", "control")) +
  xlab("Time after intervention [months]") + ylab ("BMI [kg/m²]") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10), axis.title = element_text(size = 12),
    strip.text = element_text(size = 12), legend.text = element_text(size = 10),
    legend.position = "bottom", legend.background = element_rect(colour = "grey"))

# example plot for change effect (purely descriptive)
getPalette = colorRampPalette(brewer.pal(9, "Set1"))
cgnplot <- ggplot(final, aes(x=a,y=logmFD, group=subj.ID)) +
  geom_line(aes(x=BMI, color=subj.ID))+
  geom_point(aes(x=BMI, color=subj.ID, shape=tp), size=3, alpha = 0.5)+
  facet_grid(. ~ condition)
cgnplot +
  labs(shape="Time after intervention [months]",labels=c("0","6","12")) +
  guides(color = FALSE, alpha=FALSE, size=FALSE) +
  scale_color_manual(values = getPalette(length(unique(final$subj.ID)))) +
  ylab("log(mean FD) (mm)") + xlab("BMI [kg/m²]") + xlim(30,55) +
  theme_bw() +  theme(
    axis.text = element_text(size = 10), axis.title = element_text(size = 12),
    strip.text = element_text(size = 12), legend.text = element_text(size = 10),
    legend.position = "bottom", legend.background = element_rect(colour = "grey"))

# example plot for change effect (purely descriptive)
tspag=ggplot(data=final, aes(y=cgnFD, x=cgnBMI, color=condition))+
  geom_point(size=2)+
  #geom_line(aes(color=subj.ID))+
  #geom_smooth(method = "lm", colour = "black", linetype = 1, fill = "mistyrose3" ) +
  xlab("within-subject BMI change [kg/m²]")+
  ylab("within-subject log mean FD change [mm]")+
  guides(alpha=FALSE, size=FALSE,
         color = guide_legend(override.aes = list(size=4))) +
  facet_grid(. ~ condition)
tspag + scale_color_manual(values=c("#00305E","#C00045")) +
  theme_bw() + theme(axis.text=element_text(colour = "black",size=10),
              axis.title=element_text(size=14),
              axis.text.x = element_text(size=12),
              axis.text.y = element_text(size=12),
              strip.text = element_text(size=14),
              legend.position="top",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14))
```

>>>>

```{r "tableSample", echo=FALSE}
source("./report/tables.R")
tab_sample <- mk_SampleTable(final)

tab_sample <-
  knitr::kable(
    tab_sample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Distribution of data points at months after intervention")
tab_sample
```

@@

# table_descr <- mk_tableDescr()
# table for descriptive statistics
descr <- psych::describeBy(dfw[,5:ncol(dfw)], group=dfw$condition,mat=T)
descr$predictor <- c(rep("BMI",6),rep("meanFD",6))
descr$tp <- car::recode(descr$vars, "c(1,4)='fu2';c(2,5)='fu';c(3,6)='bl'")
descr$group <- descr$group1
descr <- descr[,c("predictor","tp","group","n","mean","sd")]
descr <- descr[with(descr, order(predictor, tp)),]
descr[,c("mean","sd")] <- round(descr[,c("mean","sd")],2)
descr[c(2:6,8:12),"predictor"] <- ""
descr[c(2,4,6,8,10,12),"tp"] <- ""
rownames(descr) <- NULL

@@

```
<!-- STUDY PROCEDURE --> Subjects arrived in the morning (between 07:00 and 12:00) after an overnight fast. They underwent medical assessments including an interview, blood draw and anthropometric measurements before having a one our break for <!-- standadized??  -->breakfast. MRI scanning was done after further psychological tests (for details see @Prehn_2020).
```{r figBMIdescr, fig.align='center', out.width="90%", fig.cap="BMI over time.", echo=FALSE}
# eval = TRUE, fig.asp = 0.7, fig.width = 6
source("report/figures.R")
figBMIdescr <- mk_figBMIdescr(final)

@@

<!-- DESIGN MATRIX, vielleicht beide auch als Abbildung kurz zeigen? --> For the first model, time was introduced as factor because we did not assume strict linearity for the increase in connectivity and therefore refrained from modeling time as continuous variable (see Figure \@ref(fig:figDesignmatrix)). The resulting factorial design <!-- check: flexible factorial? --> contained one regressor for each time point per group.
```{r figDesignmatrix, fig.align = 'center', fig.ncol = 2, out.width = "50%", fig.subcap=c('Design matrix with time as categorial factor.','Design matrix with time as continuous variable.'), fig.cap="Possible design matrices of time-by-group model.", echo=FALSE}
# fig.show="hold",  out.width="40%", fig.height = 8,
source("report/figures.R")
PlotList <- mk_figDesignMatrix()

PlotList$plotA
PlotList$plotB
#gridExtra::grid.arrange(plotA, plotB, nrow=1)
```
For the second and third model, we calculated the centered mean BMI and log mean FD per subject and the intra-subject-centered BMI as proposed by @Guillaume_2014. With a model containing average BMI and longitudinal change per subject, we investigated their differential effects on the complete sample and subsequently in a exploratory fashion for the intervention group only as the effect of longitudinal change in BMI was expected to be driven by this subsample.
<!-- NUISANCE COVARIATES --> Baseline age, sex, and log mean framewise displacement (FD) were entered into the first and second model as nuisance variables. Age and sex were between-subject covariates while FD is time-varying. Mean FD was log-transformed and age was demeaned by subtracting the overall mean across subjects and time points. 
As change in FD and change in BMI share common variance [@Beyer_2019], the inclusion of log mean FD may be disputed and done optionally. For that reason, we performed each analysis separately one with mean FD (three and without. Differences in results will be reported. We consider this sensitivity analysis theoretically more meaningful than the preregistered comparison with the nuisance covariate free model and a model with four nuisance covariates (including baseline BMI).<!-- Prereg: We will perform sensitivity analysis adjusting for baseline age, sex, average of mean FD of both time points and baseline BMI -->
<!-- POST HOC  --> For a better understanding of the unique contribution of average and longitudinal change FD measures, we separately employed a third post-hoc model to disentangle the effects: $FC = between-subject FD + within-subject FD$ with nuisance covariates age and sex. As these post-hoc analyses were not preregistered, they should be considered to be exploratory.

@@

for (i in 1:nrow(final)) {
  tmp = strsplit(toString(final[i, "scan_dir"]), '/')[[1]][8]
  conf = read.csv(
    paste0("/data/pt_02161/preprocessed/resting/detailedQA/metrics/",
      tmp, "/confounds.csv"))
  tmp = cor.test(conf$DVARS, conf$FD)
  final[i, "corr_DVARS_FD"] = tmp$estimate
  final[i, "mean_DVARS"] = mean(conf$DVARS, na.rm = TRUE)
  final[i, "max_DVARS"] = max(conf$DVARS, na.rm = TRUE)
  final
}

```{r figDvarsmFD, fig.align = "center", out.width="100%", fig.cap='Summary of quality measures DVARS and mFD'}
# ,  fig.align='center', }
# eval = TRUE, fig.asp = 0.7, fig.width = 6

FigureList <- figDvarsmFD(final)
(FigureList$fig1 | FigureList$fig2) / FigureList$fig3

@@

tab_qc_fc <- mk_tableQcfc(res)
tab_qc_fc
```

@@

```{r tableBMImodel}
source("report/tables.R")
TableList <- mk_FCTables()
tab_BMImodel <- TableList[[1]]
tab_BMImodel
```

@@
